The \dealii Library, Version 9.1

### 2019-05-21 9.1/paper.tex
Added two paragraphs on rtree and parsed ct

\documentclass{ansarticle-preprint}
%\usepackage{ucs}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
%\usepackage{cite}
\usepackage{anslistings}
\usepackage{multicol}

@@

\item
  A new class \texttt{ParsedConvergenceTable} has been introduced.
  \textcolor{red}{TODO}
  \marginpar{Luca: Please expand}

@@

\item
  A new interface to \texttt{boost::geometry::index::rtree} has been added.
  \textcolor{red}{TODO}
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

@@

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$ adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For Boundary Elements Computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b}.
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16}.
\end{itemize}

>>>>

\documentclass{ansarticle-preprint}
%\usepackage{ucs}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
%\usepackage{cite}
\usepackage{anslistings}
\usepackage{multicol}
\usepackage{pdfsync}

@@

\item A new class \texttt{ParsedConvergenceTable} has been introduced
  that greatly simplifies the construction of convergence tables,
  reading the options for the generation of the table from a parameter
  file, and providing methods that, combined with a parameter file,
  allow one to generate convergence tables using one-liners in user
  codes.

@@

\item All of the elementary geometrical objects of the library (namely
  \texttt{Point<dim>}, \texttt{Segment<dim>}, and
  \texttt{BoundingBox<dim>}) have been augmented with the traits
  needed to comply with \texttt{boost::geometry} concepts. A new
  interface to \texttt{boost::geometry::index::rtree} has been added
  that simplifies the construction of spacial indices based on points,
  bounding boxes, or segments.
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

@@

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$ adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For Boundary Elements Computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b}.
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
   \item Fur uses of the \texttt{ParameterAcceptor} concept,
     \texttt{MeshWorker::ScratchData}, and
     \texttt{ParsedConvergenceTable}: \cite{SartoriGiulianiBardelloni-2018-a}.
\end{itemize}
